The Essence of Summarization\\ in Pushdown Flow Analyses\\ \textbf{Supplemental Material}

### 2014-02-27 content.tex
Changed to 10pt as per OOPSLA submission guidelines. Changed formatting to fit figures.

CFA2 is an online version of a technique called ``summarization'' from Sharir and Pnueli \citep[Chapter 7]{local:muchnick:jones:flow-analysis:1981}, which is synonymous with PDCFA's crucial ``$\epsilon$-closure graph''.
%
The online quality of the algorithm is what makes it suitable for higher-order languages.
%
Summarization algorithms need not be restricted to languages with well-bracketed calls and returns.
%
The technique is adaptable for higher precision in the common case but to still handle difficult cases such as first-class control.
%
This was shown for the \rackett{call/cc} operator in~\citet{ianjohnson:Vardoulakis2011Pushdown}.
%
This work illuminated the fact that we can harness the enhanced technology of pushdown analyses in non-pushdown models of computation.
%
Doing this sacrifices call/return matching in the general case, but in practice the precision is much better than the alternative regular model like 0-CFA would provide.
%%

@@

{
\setlength{\abovedisplayskip}{0pt}
\setlength{\belowdisplayskip}{4pt}
\setlength{\abovedisplayshortskip}{0pt}
\setlength{\belowdisplayshortskip}{8pt}
\begin{align*}
  \mexpr \in \Expr &= \svar{\mvar} \alt \sapp{\mexpr}{\mexpr} \alt \slam{\mvar}{\mexpr} \\
  \mstate \in \State &= \Expr \times \Env \times \Store \times \Kont \\
  \mval \in \Value &::= \vclo{\slam{\mvar}{\mexpr}}{\menv} \\
  \mkont \in \Kont &::= \kmt \alt \kcons{\mkframe}{\mkont} \\
  \mkframe \in \Frame &::= \kar{\mexpr,\menv} \alt \kfn{\mval} \\
  \menv \in \Env &= \Var \to \Addr \\
  \mstore \in \Store &= \Addr \to \wp(\Value) \\
  \mvar \in \Var &\text{ an infinite set} \\
  \maddr \in \Addr &\text{ an infinite set}
\end{align*}
}
%%

@@

\begin{align*}
  \mstate \in \State &= \Expr \times \Env \times \Store \times \Kont \times \KTab \times \Memo \\
  \mkont \in \Kont &::= \kmt \alt \krt{\mexpr,\menv,\mstore} \alt \kcons{\mkframe}{\mkont} \\
  \mktab \in \KTab &= Expr \times \Env\times \Store \to \wp(\Kont) \\
  \mmemo \in \Memo &= \Expr \times \Env\times \Store \to \wp(\Value \times \Store)
\end{align*}

@@

{
\setlength{\abovedisplayskip}{0pt}
\setlength{\belowdisplayskip}{4pt}
\setlength{\abovedisplayshortskip}{0pt}
\setlength{\belowdisplayshortskip}{8pt}
\begin{align*}
  \mastate \in \sa{State} &= \Expr \times \Env \times \Store \times \Kont \\
  \System &= \wp(\sa{State}) \times \wp(\sa{State} \times \sa{State}) \times \KTab \times \Memo \\
  {\mathcal F} &: \sa{\State} \to \System \to \System
\end{align*}
\begin{align*}
  {\mathcal F}(\mastate_0)(\emptyset, R, \mktab, \mmemo) &= (\emptyset, R, \mktab, \mmemo) \\
  {\mathcal F}(\mastate_0)(F\uplus\set{\mastate}, R, \mktab, \mmemo) &= (F\cup F', R \cup R', \mktab', \mmemo') \\
  \text{where } I &= \setbuild{\mstate'}{\wn(\mastate,\mktab,\mmemo) \stepto \mstate'} \\
                \wn(\tpl{\mexpr,\menv,\mstore,\mkont},\mktab,\mmemo)
                   &= \tpl{\mexpr,\menv,\mstore,\mkont,\mktab,\mmemo}
\end{align*}
\begin{align*}
    R' &= \setbuild{(\mastate,\mastate')}{\wn(\mastate', \_, \_) \in I \wedge \mastate\nequiv\tpl{\mval,\mstore,\krt{\mctx}}} \cup \set{\mastate_0}\\
    \mktab' &=  \bigsqcup\setbuild{\mktab'}{\wn(\_, \mktab', \_) \in I} \\
    \mmemo' &= \bigsqcup\setbuild{\mmemo'}{\wn(\_, \_, \mmemo') \in I} \\
    F' &= \setbuild{\mastate'}{\wn(\mastate', \_, \_) \in I} \setminus (\pi_1 R \cup \pi_2 R)
  \end{align*}
}
%%

%%
A $\System$ embodies the reductions seen disregarding the administrative pop steps, $R$, the frontier set of states yet to analyze, $F$, the continuation table $\mktab$ and the memo table $\mmemo$.
%
We define $\pi_1$ and $\pi_2$ as the pointwise lifting of the left and right projections out of a pair, respectively.
% Note: Only if widened store.{
%
%The memo table need only map to values, since the global store will always subsume the store that would otherwise be mapped.
%
%All the states in the frontier are stepped with the current store, after which the next store is the least upper bound of all the resulting stores.
%
%The next frontier contains only states resulting from stepping the previous frontier that we haven't seen at this next store.}
%
The least fixed-point of ${\mathcal F}(\tpl{\mexpr,\bot,\bot,\kmt})$ is the analysis of closed expression $\mexpr$.
%
Systematic techniques for a performant implementation can be found in \citet{ianjohnson:oaam:icfp2013}.
%

@@

Abstract garbage collection~\citep{dvanhorn:Might:2006:GammaCFA} is a powerful technique for regaining precision in an abstract interpretation.
%
The followup to PDCFA~\citep{dvanhorn:Earl2012Introspective} that allows inspecting the stack in order to perform sound GC introduces an entirely new class of automata for this one purpose.
%
In our view with tabular semantics, the GC story mimics the simplicity of GC in the regular setting, without the detour into automata theory.
%
We follow the GC style of \citet{dvanhorn:Might:2006:GammaCFA} with a stop-and-copy collector.
%
Address reachability is in terms of a base ``touches'' function, $\touches$.
%
Entries in $\mktab$ might be circular, so we compute the continuation frames in a fixed-point before computing touched addresses:
\begin{center}
  \,
    $\touchesk{\mkont}(\mktab) = \setbuild{\maddr}{\mkont \rightsquigarrow_\mktab^*\maddr}$
\\[4pt]
  \begin{minipage}{0.5\linewidth}
    $\touchesf(\kar{\mexpr,\menv}) = \mathit{range}(\menv|_{\mathit{fv}(\mexpr)})$
  \end{minipage}
  \begin{minipage}{0.4\linewidth}
    $\touchesf(\kfn{\mval}) = \touches(\mval)$
  \end{minipage}
\end{center}
\begin{mathpar}
  \inferrule{ }{\kcons{\mkframe}{\mkont} \rightsquigarrow_\mktab \mkont}
  \quad
  \inferrule{\maddr \in \touchesf(\mkframe)}{\kcons{\mkframe}{\mkont} \rightsquigarrow_\mktab \maddr}
  \quad
  \inferrule{\mkont \rightsquigarrow_\mktab \mkont'}{\kcons{\mkframe}{\mkont} \rightsquigarrow_\mktab \mkont'}
  \quad
  \inferrule{\mkont \rightsquigarrow_\mktab \maddr}{\kcons{\mkframe}{\mkont} \rightsquigarrow_\mktab \maddr}
%  \inferrule{\mkont \rightsquigarrow_\mktab (\mkont' \text{ or } \maddr)}{\kcons{\mkframe}{\mkont} \rightsquigarrow_\mktab (\mkont' \text{ or } \maddr)}
  \quad
  \inferrule{\mkont \in \mktab(\mctx)}{\krt{\mctx} \rightsquigarrow_\mktab \mkont}
\end{mathpar}

@@

\begin{align*}
  \reaches(\mathit{root}, \mstore) = \setbuild{b}{\maddr \in \mathit{root}, \maddr \rightsquigarrow_\mstore^* b}
   \quad
               \inferrule{\mval \in \mstore(\maddr) \\
                             b \in \touches(\mval)}
                            {\maddr \rightsquigarrow_\mstore b}
\end{align*}

@@

\begin{figure}
  \centering
  $\mstate \stepto \mstate' \text{ where } \maddr = \alloc(\mstate)$ \\
  \begin{tabular}{r|l}
    \hline
% variable lookup
    $\tpl{\svar[\mlab]{\mvar}, \menv, \mstore, \mframe, \mkont}$
    &
    $\tpl{\mval,\mstore,\mframe',\mkont}$ if $(\mframe', \mval) \in \lookup(\mstore,\mframe,\menv(\mvar),\mlab)$
    \\
% % application
%     $\tpl{(\sapp{\mexpri0}{\mexpri1}, \menv), \mstore, \mframe, \mkont}$
%     &
%     $\tpl{(\mexpri0, \menv), \mstore, \mframe, \kar{\mexpri1,\menv,\mkont}}$
%     \\
% % argument evaluation
%     $\tpl{\mval, \mstore, \mframe, \kar{\mexpr,\menv,\mkont}}$
%     &
%     $\tpl{(\mexpr, \menv), \mstore, \mframe, \kfn{\mval, \mkont}}$
%     \\
% function call
    $\tpl{\mval,\mstore,\mframe,\kcons{\kfn{\vclo{\slam{\mvar}{\mexpr}}{\menv}}}{\mkont}}$
    &
    $\tpl{\mexpr, \extm{\menv}{\mvar}{\maddr}, \mstore', \mframe', \kcons{\kpush{\mframe}}{\mkont}}$
    \\ & where $(\mstore',\mframe') = \bind(\mstore,\maddr,\mvar,\mval)$
    \\
    $\tpl{\mval,\mstore,\mframe,\kcons{\kpush{\mframe'}}{\mkont}}$
    &
    $\tpl{\mval,\mstore,\mframe',\mkont}$
  \end{tabular}
  \caption{The CES$\xi$K machine significant rules}
  \label{fig:frame-semantics}
\end{figure}

@@

Sidestepping fake rebinding does not need to be restricted to stackable references, but that is what CFA2 does.
%
As soon as the non-determinism has been determined, we could extend the stack frame so any subsequent reference means what it meant previously in the function.
%
Look-up would then always try the stack frame before falling back on the heap (this must be limited to immutable addresses).
%%

@@

\begin{center}
  \begin{minipage}{0.45\linewidth}
    \begin{align*}
      \mstate \in \State &::= \tpl{\mpoint, \mstore, \mkont, \mmkont} \\
      \mpoint \in \Point &::= (\mexpr, \menv) \alt \mval
    \end{align*}
  \end{minipage}
  \begin{minipage}{0.50\linewidth}
    \begin{align*}
      \mval \in \Value &::= \vclo{\slam{\mvar}{\mexpr}}{\menv} \alt \vcomp{\mkont} \\
      \mmkont \in \MKont &::= \kmt \alt \mkapp{\mkont}{\mmkont}
    \end{align*}
  \end{minipage}
\end{center}
\begin{figure}
  \centering
  $\mstate \stepto \mstate' \text{ where } \maddr = \alloc(\mstate)$ \\
  \begin{tabular}{r|l}%{r|ll}
    \hline
% Reset
    $\tpl{\sreset{\mexpr}, \menv, \mstore, \mkont, \mmkont}$
    &
    $\tpl{\mexpr, \menv, \mstore, \kmt, \mkapp{\mkont}{\mmkont}}$
%    & \textsc{[push prompt]}
    \\
% Pop prompt
    $\tpl{\mval, \mstore, \kmt, \mkapp{\mkont}{\mmkont}}$
    &
    $\tpl{\mval, \mstore, {\mkont}, {\mmkont}}$
%    & \textsc{[pop prompt]}
    \\
% Shift
    $\tpl{\sshift{\mvar}{\mexpr}, \menv, \mstore, \mkont, \mmkont}$
    &
    $\tpl{\mexpr, \extm{\menv}{\mvar}{\maddr}, \mstore',\kmt,\mmkont}$
%    & \textsc{[capture continuation]}
    \\ & where $\mstore' = \joinone{\mstore}{\maddr}{\vcomp{\mkont}}$
    \\
% continuation call
    $\tpl{\mval,\mstore,\kcons{\kfn{\vcomp{\mkont'}}}{\mkont}, \mmkont}$
    &
    $\tpl{\mval, \mstore, \mkont', \mkapp{\mkont}{\mmkont}}$
%    & \textsc{[compose continuation]}
  \end{tabular}  
  \caption{Machine semantics for shift/reset}
  \label{fig:shift-reset}
\end{figure}

@@

\newcommand{\replacectx}{\hat\mkont} %\mathit{replace}\mstore
\newcommand{\addstore}{\hat\mmktab} % \mathit{add}\mstore
\begin{center}
  $\approximate(\mkont, \mmktab, \maddr) = (\replacectx(\mkont), \addstore(\mkont)) \text{ where}$\\
  \begin{minipage}{0.45\linewidth}
    \begin{align*}
      \replacectx(\kmt) &= \kmt \\
      \replacectx(\krt{(\mexpr,\menv,\ldots)}) &= \krt{(\mexpr,\menv,\maddr)} \\
      \replacectx(\kcons{\mkframe}{\mkont}) &=
      \kcons{\mkframe}{\replacectx(\mkont)}
    \end{align*}
  \end{minipage}
  \begin{minipage}{0.50\linewidth}
    \begin{align*}
      \addstore(\kmt) &= \mmktab \\
      \addstore(\krt{(\mexpr,\menv,\mstore,\mmktab')}) &= \joinone{\mmktab}{\maddr}{\mstore}\sqcup \mmktab' \\
      \addstore(\krt{(\mexpr,\menv,\maddr')}) &= \joinm{\mmktab}{\maddr}{\mmktab(\maddr')} \\
      \addstore(\kcons{\mkframe}{\mkont}) &= \addstore(\mkont)
    \end{align*}
  \end{minipage}
\end{center}
%
If the context in an $\rt$ continuation is approximate, we must return to all the continuations known for all the contexts it approximates:
\begin{align*}
  \returns(\mmktab, \mktab, (\mexpr,\menv, \mstore, \mmktab')) &= \mktab(\mexpr,\menv, \mstore, \mmktab') \\
  \returns(\mmktab, \mktab, (\mexpr,\menv, \maddr)) &=
    \bigcup\setbuild{\mktab(\mexpr,\menv,\mstore,\mmktab')}{(\mstore \in \mmktab(\maddr), \mmktab' \sqsubseteq \mmktab}
\end{align*}

At returns, the memo table must add the result to all represented contexts:
\begin{align*}
  \memoize(\mmktab, \mktab, (\mexpr,\menv, \mstore', \mmktab'), \mathit{out}) &=
  [(\mexpr,\menv, \mstore',\mmktab') \mapsto \set{{\mathit{out}}}] \\
  \memoize(\mmktab, \mktab, (\mexpr,\menv, \maddr), \mathit{out}) &= [\mctx \mapsto \set{\mathit{out}} : \mctx \in \dom(\mktab) \cap C] \\
    \text{where } C &= \setbuild{(\mexpr,\menv, \mstore', \mmktab')}{\mstore' \in \mmktab(\maddr), \mmktab' \sqsubseteq \mmktab}
\end{align*}

@@

\mbox{\hphantom{\Scribtexttt{xxxxxxx}}}\RktPn{[}\RktSym{g}\mbox{\hphantom{\Scribtexttt{x}}}\RktPn{(}\RktSym{$\lambda$}\mbox{\hphantom{\Scribtexttt{x}}}\RktPn{(}\RktSym{z}\mbox{\hphantom{\Scribtexttt{x}}}\RktSym{h}\RktPn{)}\mbox{\hphantom{\Scribtexttt{x}}}\RktPn{(}\RktSym{h}\mbox{\hphantom{\Scribtexttt{x}}}\RktPn{(}\RktSym{f}\mbox{\hphantom{\Scribtexttt{x}}}\RktSym{z}\mbox{\hphantom{\Scribtexttt{x}}}\RktPn{(}\RktSym{$\lambda$}\mbox{\hphantom{\Scribtexttt{x}}}\RktPn{(}\RktSym{fv}\RktPn{)}\mbox{\hphantom{\Scribtexttt{x}}}\RktPn{(}\RktSym{id}\mbox{\hphantom{\Scribtexttt{x}}}\RktSym{fv}\mbox{\hphantom{\Scribtexttt{x}}}\RktPn{(}\RktSym{$\lambda$}\mbox{\hphantom{\Scribtexttt{x}}}\RktPn{(}\RktSym{i}\RktPn{)}\mbox{\hphantom{\Scribtexttt{x}}}\RktSym{i}\RktPn{)}\RktPn{)}\RktPn{)}\RktPn{)}\RktPn{)}\RktPn{)}\RktPn{]}\RktPn{)}

>>>>

CFA2 is an online version of a technique called ``summarization'' from Sharir and Pnueli \citep[Chapter 7]{local:muchnick:jones:flow-analysis:1981}, which is synonymous with PDCFA's crucial ``$\epsilon$-closure graph''.
%
The online quality of the algorithm is what makes it suitable for higher-order languages, since CFA essentially interprets the program for each discovered state to build the model on the fly.
%
Summarization algorithms need not be restricted to languages with well-bracketed calls and returns.
%
The technique is adaptable for higher precision in the common case but to still handle difficult cases such as first-class control.
%
This was shown for the \rackett{call/cc} operator in~\citet{ianjohnson:Vardoulakis2011Pushdown}.
%
This work illuminated the fact that we can harness the enhanced technology of pushdown analyses in non-pushdown models of computation.
%
Doing this sacrifices call/return matching in the general case, but in practice the precision is much better than the alternative regular model like 0-CFA would provide.
%%

@@

{
\setlength{\abovedisplayskip}{0pt}
\setlength{\belowdisplayskip}{4pt}
\setlength{\abovedisplayshortskip}{0pt}
\setlength{\belowdisplayshortskip}{8pt}
\begin{align*}
  \mexpr \in \Expr &= \svar{\mvar} \alt \sapp{\mexpr}{\mexpr} \alt \slam{\mvar}{\mexpr} \\
  \mstate \in \State &::= \tpl{\mexpr,\menv,\mstore,\mkont} \\
  \mval \in \Value &::= \vclo{\slam{\mvar}{\mexpr}}{\menv} \\
  \mkont \in \Kont &::= \kmt \alt \kcons{\mkframe}{\mkont} \\
  \mkframe \in \Frame &::= \kar{\mexpr,\menv} \alt \kfn{\mval} \\
  \menv \in \Env &= \Var \to \Addr \\
  \mstore \in \Store &= \Addr \to \wp(\Value) \\
  \mvar \in \Var &\text{ an infinite set} \\
  \maddr \in \Addr &\text{ an infinite set}
\end{align*}
}
%%

@@

\begin{align*}
  \mstate \in \State &::= \tpl{\mexpr,\menv,\mstore,\mkont,\mktab,\mmemo} \\
  \mkont \in \Kont &::= \kmt \alt \krt{\mexpr,\menv,\mstore} \alt \kcons{\mkframe}{\mkont} \\
  \mktab \in \KTab &= Expr \times \Env\times \Store \to \wp(\Kont) \\
  \mmemo \in \Memo &= \Expr \times \Env\times \Store \to \wp(\Value \times \Store)
\end{align*}

@@

{
\setlength{\abovedisplayskip}{0pt}
\setlength{\belowdisplayskip}{4pt}
\setlength{\abovedisplayshortskip}{0pt}
\setlength{\belowdisplayshortskip}{8pt}
\begin{align*}
  \mastate \in \sa{State} &::= \tpl{\mexpr,\menv,\mstore,\mkont} \\
  \System &= \wp(\sa{State}) \times \wp(\sa{State} \times \sa{State}) \times \KTab \times \Memo \\
  {\mathcal F} &: \sa{\State} \to \System \to \System
\end{align*}
\begin{align*}
  {\mathcal F}(\mastate_0)(\emptyset, R, \mktab, \mmemo) &= (\emptyset, R, \mktab, \mmemo) \\
  {\mathcal F}(\mastate_0)(F\uplus\set{\mastate}, R, \mktab, \mmemo) &= (F\cup F', R \cup R', \mktab', \mmemo') \\
  \text{where } I &= \setbuild{\mstate'}{\wn(\mastate,\mktab,\mmemo) \stepto \mstate'} \\
                \wn(\tpl{\mexpr,\menv,\mstore,\mkont},\mktab,\mmemo)
                   &= \tpl{\mexpr,\menv,\mstore,\mkont,\mktab,\mmemo}
\end{align*}
\begin{align*}
    R' &= \setbuild{(\mastate,\mastate')}{\wn(\mastate', \_, \_) \in I \wedge \mastate\nequiv\tpl{\mval,\mstore,\krt{\mctx}}} \cup \set{\mastate_0}\\
    \mktab' &=  \bigsqcup\setbuild{\mktab'}{\wn(\_, \mktab', \_) \in I} \\
    \mmemo' &= \bigsqcup\setbuild{\mmemo'}{\wn(\_, \_, \mmemo') \in I} \\
    F' &= \setbuild{\mastate'}{\wn(\mastate', \_, \_) \in I} \setminus (\pi_1 R \cup \pi_2 R)
  \end{align*}
}
%%

%%
A $\System$ embodies the reductions seen disregarding the administrative pop steps, $R$, the frontier set of states yet to analyze, $F$, the continuation table $\mktab$ and the memo table $\mmemo$.
%
We define $\pi_1$ and $\pi_2$ as the pointwise lifting of the left and right projections out of a pair, respectively.
% Note: Only if widened store.{
%
%The memo table need only map to values, since the global store will always subsume the store that would otherwise be mapped.
%
%All the states in the frontier are stepped with the current store, after which the next store is the least upper bound of all the resulting stores.
%
%The next frontier contains only states resulting from stepping the previous frontier that we haven't seen at this next store.}
%
The least fixed-point of ${\mathcal F}(\tpl{\mexpr,\bot,\bot,\kmt})$ is the analysis of closed expression $\mexpr$.
%
Note the ordering on systems is pointwise, so the bottom element is $(\emptyset,\emptyset,\bot,\bot)$, which we'll call $\mathit{sys}_0$.
%
Systematic techniques for a performant implementation can be found in \citet{ianjohnson:oaam:icfp2013}.
%

@@

Abstract garbage collection~\citep{dvanhorn:Might:2006:GammaCFA} is a powerful technique for regaining precision in an abstract interpretation.
%
The followup to PDCFA~\citep{dvanhorn:Earl2012Introspective} that allows inspecting the stack in order to perform sound GC introduces an entirely new class of automata for this one purpose.
%
In our view with tabular semantics, the GC story mimics the simplicity of GC in the regular setting, without the detour into automata theory.
%
We follow the GC style of \citet{dvanhorn:Might:2006:GammaCFA} with a stop-and-copy collector.
%
Address reachability is in terms of a base ``touches'' function, $\touches$.
%
Entries in $\mktab$ might be circular, so we compute the continuation frames in a fixed-point before computing touched addresses:
\begin{center}
  \,
    $\touchesk{\mkont}(\mktab) = \setbuild{\maddr}{\mkont \rightsquigarrow_\mktab^*\maddr}$
\\[4pt]
  \begin{minipage}{0.55\linewidth}
    $\touchesf(\kar{\mexpr,\menv}) = \mathit{range}(\menv|_{\mathit{fv}(\mexpr)})$
  \end{minipage}
  \begin{minipage}{0.4\linewidth}
    $\touchesf(\kfn{\mval}) = \touches(\mval)$
  \end{minipage}
\end{center}
\begin{mathpar}
  \inferrule{ }{\kcons{\mkframe}{\mkont} \rightsquigarrow_\mktab \mkont}
  \quad
  \inferrule{\maddr \in \touchesf(\mkframe)}{\kcons{\mkframe}{\mkont} \rightsquigarrow_\mktab \maddr}
  \quad
  \inferrule{\mkont \rightsquigarrow_\mktab \mkont'}{\kcons{\mkframe}{\mkont} \rightsquigarrow_\mktab \mkont'}
  \quad
  \inferrule{\mkont \rightsquigarrow_\mktab \maddr}{\kcons{\mkframe}{\mkont} \rightsquigarrow_\mktab \maddr}
%  \inferrule{\mkont \rightsquigarrow_\mktab (\mkont' \text{ or } \maddr)}{\kcons{\mkframe}{\mkont} \rightsquigarrow_\mktab (\mkont' \text{ or } \maddr)}
  \\
  \inferrule{\mkont \in \mktab(\mctx)}{\krt{\mctx} \rightsquigarrow_\mktab \mkont}
\end{mathpar}

@@

\begin{center}
  $\reaches(\mathit{root}, \mstore) = \setbuild{b}{\maddr \in \mathit{root}, \maddr \rightsquigarrow_\mstore^* b}$
\end{center}
\begin{mathpar}
  \inferrule{\mval \in \mstore(\maddr) \\
    b \in \touches(\mval)}
  {\maddr \rightsquigarrow_\mstore b}
\end{mathpar}

@@

\begin{figure}
  \centering
  $\mstate \stepto \mstate' \text{ where } \maddr = \alloc(\mstate)$ \\
  \begin{tabular}{r|l}
    \hline
% variable lookup
    $\tpl{\svar[\mlab]{\mvar}, \menv, \mstore, \mframe, \mkont}$
    &
    $\tpl{\mval,\mstore,\mframe',\mkont}$
    \\ & if $(\mframe', \mval) \in \lookup(\mstore,\mframe,\menv(\mvar),\mlab)$
    \\
% % application
%     $\tpl{(\sapp{\mexpri0}{\mexpri1}, \menv), \mstore, \mframe, \mkont}$
%     &
%     $\tpl{(\mexpri0, \menv), \mstore, \mframe, \kar{\mexpri1,\menv,\mkont}}$
%     \\
% % argument evaluation
%     $\tpl{\mval, \mstore, \mframe, \kar{\mexpr,\menv,\mkont}}$
%     &
%     $\tpl{(\mexpr, \menv), \mstore, \mframe, \kfn{\mval, \mkont}}$
%     \\
% function call
    $\tpl{\mval,\mstore,\mframe,\kcons{\kfn{\vclo{\slam{\mvar}{\mexpr}}{\menv}}}{\mkont}}$
    &
    $\tpl{\mexpr, \extm{\menv}{\mvar}{\maddr}, \mstore', \mframe', \kcons{\kpush{\mframe}}{\mkont}}$
    \\ & where $(\mstore',\mframe') = \bind(\mstore,\maddr,\mvar,\mval)$
    \\
    $\tpl{\mval,\mstore,\mframe,\kcons{\kpush{\mframe'}}{\mkont}}$
    &
    $\tpl{\mval,\mstore,\mframe',\mkont}$
  \end{tabular}
  \caption{The CES$\xi$K machine significant rules}
  \label{fig:frame-semantics}
\end{figure}

@@

Sidestepping fake rebinding does not need to be restricted to stackable references, but that is what CFA2 does.
%
As soon as the non-determinism has been determined, we could extend the stack frame so any subsequent reference means what it meant previously in the function.
%
Look-up would then always try the stack frame before falling back on the heap, though this must be limited to immutable addresses.
%%

@@

\begin{center}
  \begin{minipage}{0.45\linewidth}
    \begin{align*}
      \mstate \in \State &::= \tpl{\mpoint, \mstore, \mkont, \mmkont} \\
      \mpoint \in \Point &::= (\mexpr, \menv) \alt \mval
    \end{align*}
  \end{minipage}
  \begin{minipage}{0.50\linewidth}
    \begin{align*}
      \mval \in \Value &::= \vclo{\slam{\mvar}{\mexpr}}{\menv} \alt \vcomp{\mkont} \\
      \mmkont \in \MKont &::= \kmt \alt \mkapp{\mkont}{\mmkont}
    \end{align*}
  \end{minipage}
\end{center}
\begin{figure}
  \centering
  $\mstate \stepto \mstate' \text{ where } \maddr = \alloc(\mstate)$ \\
  \begin{tabular}{r|l}%{r|ll}
    \hline
% Reset
    $\tpl{\sreset{\mexpr}, \menv, \mstore, \mkont, \mmkont}$
    &
    $\tpl{\mexpr, \menv, \mstore, \kmt, \mkapp{\mkont}{\mmkont}}$
%    & \textsc{[push prompt]}
    \\
% Pop prompt
    $\tpl{\mval, \mstore, \kmt, \mkapp{\mkont}{\mmkont}}$
    &
    $\tpl{\mval, \mstore, {\mkont}, {\mmkont}}$
%    & \textsc{[pop prompt]}
    \\
% Shift
    $\tpl{\sshift{\mvar}{\mexpr}, \menv, \mstore, \mkont, \mmkont}$
    &
    $\tpl{\mexpr, \extm{\menv}{\mvar}{\maddr}, \mstore',\kmt,\mmkont}$
%    & \textsc{[capture continuation]}
    \\ where & $\mstore' = \joinone{\mstore}{\maddr}{\vcomp{\mkont}}$
    \\
% continuation call
    $\tpl{\mval,\mstore,\kcons{\kfn{\vcomp{\mkont'}}}{\mkont}, \mmkont}$
    &
    $\tpl{\mval, \mstore, \mkont', \mkapp{\mkont}{\mmkont}}$
%    & \textsc{[compose continuation]}
  \end{tabular}  
  \caption{Machine semantics for shift/reset}
  \label{fig:shift-reset}
\end{figure}

@@

\newcommand{\replacectx}{\hat\mkont} %\mathit{replace}\mstore
\newcommand{\addstore}{\hat\mmktab} % \mathit{add}\mstore
\begin{center}
  $\approximate(\mkont, \mmktab, \maddr) = (\replacectx(\mkont), \addstore(\mkont)) \text{ where}$\\
  \begin{minipage}{0.45\linewidth}
    \begin{align*}
      \replacectx(\kmt) &= \kmt \\
      \replacectx(\krt{(\mexpr,\menv,\ldots)}) &= \krt{(\mexpr,\menv,\maddr)} \\
      \replacectx(\kcons{\mkframe}{\mkont}) &=
      \kcons{\mkframe}{\replacectx(\mkont)}
    \end{align*}
  \end{minipage}
  \begin{minipage}{0.50\linewidth}
    \begin{align*}
      \addstore(\kmt) &= \mmktab \\
      \addstore(\krt{(\mexpr,\menv,\mstore,\mmktab')}) &= \joinone{\mmktab}{\maddr}{\mstore}\sqcup \mmktab' \\
      \addstore(\krt{(\mexpr,\menv,\maddr')}) &= \joinm{\mmktab}{\maddr}{\mmktab(\maddr')} \\
      \addstore(\kcons{\mkframe}{\mkont}) &= \addstore(\mkont)
    \end{align*}
  \end{minipage}
\end{center}
%
If the context in an $\rt$ continuation is approximate, we must return to all the continuations known for all the contexts it approximates:
\begin{align*}
  &\returns(\mmktab, \mktab, (\mexpr,\menv, \mstore, \mmktab')) = \mktab(\mexpr,\menv, \mstore, \mmktab') \\
  &\returns(\mmktab, \mktab, (\mexpr,\menv, \maddr)) =
    \bigcup\setbuild{\mktab(\mexpr,\menv,\mstore,\mmktab')}{\mstore \in \mmktab(\maddr), \mmktab' \sqsubseteq \mmktab}
\end{align*}

At returns, the memo table must add the result to all represented contexts:
\newcommand{\res}{m}
\begin{align*}
  &\memoize(\mmktab, \mktab, (\mexpr,\menv, \mstore', \mmktab'), \res) =
  [(\mexpr,\menv, \mstore',\mmktab') \mapsto \set{{\res}}] \\
  &\memoize(\mmktab, \mktab, (\mexpr,\menv, \maddr), \res) = [\mctx \mapsto \set{\res} : \mctx \in \dom(\mktab) \cap C] \\
  &\text{where } C = \setbuild{(\mexpr,\menv, \mstore', \mmktab')}{\mstore' \in \mmktab(\maddr), \mmktab' \sqsubseteq \mmktab}
\end{align*}

@@

\mbox{\hphantom{\Scribtexttt{xxxxxxx}}}\RktPn{[}\RktSym{g}\mbox{\hphantom{\Scribtexttt{x}}}\RktPn{(}\RktSym{$\lambda$}\mbox{\hphantom{\Scribtexttt{x}}}\RktPn{(}\RktSym{z}\mbox{\hphantom{\Scribtexttt{x}}}\RktSym{h}\RktPn{)}
\\\mbox{\hphantom{\Scribtexttt{xxxxxxxxxxx}}}\RktPn{(}\RktSym{h}\mbox{\hphantom{\Scribtexttt{x}}}\RktPn{(}\RktSym{f}\mbox{\hphantom{\Scribtexttt{x}}}\RktSym{z}\mbox{\hphantom{\Scribtexttt{x}}}\RktPn{(}\RktSym{$\lambda$}\mbox{\hphantom{\Scribtexttt{x}}}\RktPn{(}\RktSym{fv}\RktPn{)}
\\\mbox{\hphantom{\Scribtexttt{xxxxxxxxxxxxxxxxxxxx}}}\RktPn{(}\RktSym{id}\mbox{\hphantom{\Scribtexttt{x}}}\RktSym{fv}\mbox{\hphantom{\Scribtexttt{x}}}\RktPn{(}\RktSym{$\lambda$}\mbox{\hphantom{\Scribtexttt{x}}}\RktPn{(}\RktSym{i}\RktPn{)}\mbox{\hphantom{\Scribtexttt{x}}}\RktSym{i}\RktPn{)}\RktPn{)}\RktPn{)}\RktPn{)}\RktPn{)}\RktPn{)}\RktPn{]}\RktPn{)}
